Application of Network Flow and Linear Programming to Scheduling of Clinicians

### 2019-07-30 paper/paper.results.tex
Fix past->present tense in results for consistency

\subsection{Software}
We developed a software package with a user interface that implements the above LP problem and allows configuration of clinicians at [ref \ref{???}], to be used by the ID division at St. Michael's Hospital. The software was used to generate the results in the following sections, using real data as well as simulated data as input.

\subsection{Infectious Diseases Division}
We used clinician time-off requests and minimum/maximum requirements from 2015-2018 as input data for the LP problem. Tables \ref{tbl:2017-schedule-comparison}, \ref{tbl:2018-schedule-comparison}, \ref{??}, \ref{??} present the optimal schedule generated using the software as well as the manually created schedule, color-coded to distinguish between the different clinicians assigned.

@@

We began by evaluating the runtime in a single-division department, with an increasing number of clinicians, over a 1-year time-span. Figure \ref{fig:avg-runtime-clinicians} shows the average runtime in seconds of 10 runs, for different numbers of clinicians, $C = \{5, 10, 15, 25, 50, 100\}$. From the graph, we can see that the LP formulation performs extremely well on a typical hospital department with no more than 30 clinicians [ref \ref{??}], and can even handle busier departments with upwards of 100 clinicians. \\

@@

Next we evaluated the effect of increasing the number of departments. Figure \ref{fig:avg-runtime-divisions} shows the average runtime for a department with a 10 clinicians, and a range of divisions, $D = \{1, 2, 3\}$. We can see that increasing the number of divisions even by 2 greatly affects the runtime. The LP solver had significant trouble when we increased the number of divisions further, making it impractical to quickly generate schedules for departments with many divisions. \\

@@

We plotted the effect of an increasing number of requests per clinician on the average runtime of the LP solver in figure \ref{fig:avg-runtime-requests}. We ran the program on a single-division department with 10 clinicians, and $R = \abs{\mathcal{WR}} + \abs{\mathcal{BR}} = \{1, 2, 3, 5, 10\}$ non-overlapping requests per clinician. The increase in the number of requests did not affect the runtime of the LP solver, indicating that it can accommodate a lot of flexibility in clinician requests. \\

>>>>

\subsection{Software}
We develop a software package with a user interface that implements the above LP problem and allows configuration of clinicians at [ref \ref{???}], to be used by the ID division at St. Michael's Hospital. The software was used to generate the results in the following sections, using real data as well as simulated data as input.

\subsection{Infectious Diseases Division}
We use clinician time-off requests and minimum/maximum requirements from 2015-2018 as input data for the LP problem. Tables \ref{tbl:2017-schedule-comparison}, \ref{tbl:2018-schedule-comparison}, \ref{??}, \ref{??} present the optimal schedule generated using the software as well as the manually created schedule, color-coded to distinguish between the different clinicians assigned.

@@

We begin by evaluating the runtime in a single-division department, with an increasing number of clinicians, over a 1-year time-span. Figure \ref{fig:avg-runtime-clinicians} shows the average runtime in seconds of 10 runs, for different numbers of clinicians, $C = \{5, 10, 15, 25, 50, 100\}$. From the graph, we can see that the LP formulation performs extremely well on a typical hospital department with no more than 30 clinicians [ref \ref{??}], and can even handle busier departments with upwards of 100 clinicians. \\

@@

Next we evaluate the effect of increasing the number of departments. Figure \ref{fig:avg-runtime-divisions} shows the average runtime for a department with a 10 clinicians, and a range of divisions, $D = \{1, 2, 3\}$. We can see that increasing the number of divisions even by 2 greatly affects the runtime. The LP solver had significant trouble when we increased the number of divisions further, making it impractical to quickly generate schedules for departments with many divisions. \\

@@

We plot the effect of an increasing number of requests per clinician on the average runtime of the LP solver in figure \ref{fig:avg-runtime-requests}. We run the program on a single-division department with 10 clinicians, and $R = \abs{\mathcal{WR}} + \abs{\mathcal{BR}} = \{1, 2, 3, 5, 10\}$ non-overlapping requests per clinician. The increase in the number of requests did not affect the runtime of the LP solver, indicating that it can accommodate a lot of flexibility in clinician requests. \\
